Cybercrime and Online Video Games

### 2019-12-14 paper/paper.tex
Expand web scraping section

\subsection{Web Scraping}
Web scraping refers to the process of extracting data from web pages, and the 
term typically implies the automation of this process. Data extracted from web
pages will then be parsed to be usable. Often, websites will not provide 
easily accessible data sets of the website content, which means that a 
web scraping program must be written to extract the relevant information from
the HTML present on the page. Given the sheer volume of information that must
be collected, the best action is to implement our own program to scrape data 
from Hack Forums.

>>>>

\subsection{Web Scraping}
Web scraping refers to the process of extracting data from web pages, and the 
term typically implies the automation of this process. Data extracted from web
pages will then be parsed to be usable. Often, websites will not provide 
easily accessible data sets of the website content, which means that a 
web scraping program must be written to extract the relevant information from
the Hyptertext Markup Language (HTML) present on the page. Unfortnuately, 
scraping the data is not as simple as traversing the pages and downloadsing the 
web page's HTML files and manullay inspecting them. Due to the large amount of 
threads and comments that must be analyzed, a program needs to be created to 
find the comment texts of each page and aggregate the comments in one file. 
And since data aggregation can be automated, the traversal of the website 
should be too. In most cases where a functional Application Programming Interface
(API) is not available, a web scraping program has to analyze the hyperlinks
available on the page to identify further pages to traverse and collect data.
Since forum style websites are neatly categorized for ease of use by visitors, 
traversal is not complicated.
